---
title: "Flow analysis"
output: html_notebook
---

Load Clusters of complex stimulus mapped to the Clusters to basic stimulus
```{r}
library(R.matlab)
data <- readMat('D:/Pictures/processed/Flow/complex_AlltrialsinOne/BasicClusters.mat')
composite_ts <- data$Test
composite_ts <- data.frame(t(composite_ts))
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.
```{r}
library(forecast)
library(MSBVAR)
ts1 <- scale(composite_ts)

select.lags<-function(x,y,max.lag=8) {
  y<-as.numeric(y)
  y.lag<-embed(y,max.lag+1)[,-1,drop=FALSE]
  x.lag<-embed(x,max.lag+1)[,-1,drop=FALSE]

  t<-tail(seq_along(y),nrow(y.lag))

  ms=lapply(1:max.lag,function(i) lm(y[t]~y.lag[,1:i]+x.lag[,1:i]))

  pvals<-mapply(function(i) anova(ms[[i]],ms[[i-1]])[2,"Pr(>F)"],max.lag:2)
  ind<-which(pvals<0.05)[1]
  ftest<-ifelse(is.na(ind),1,max.lag-ind+1)

  aic<-as.numeric(lapply(ms,AIC))
  bic<-as.numeric(lapply(ms,BIC))
  structure(list(ic=cbind(aic=aic,bic=bic),pvals=pvals,
    selection=list(aic=which.min(aic),bic=which.min(bic),ftest=ftest)))
}

s<-select.lags(ts1[,4],ts1[,1],50)
```

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

```{r}
library('strucchange')
library('vars')
library('tseries')
library('urca')
ADF_KPSS <- matrix(nrow=2,ncol = length(composite_ts))
for (i in 1:length(composite_ts)) {
  temp <- adf.test(ts1[,i])
  temp2 <- kpss.test(ts1[,i])
  ADF_KPSS[1,i]<- temp$p.value
  ADF_KPSS[2,i]<-temp2$p.value
}
ADF_KPSS
```

since KPSS p-value <0.05 means not stationary, so let's dif

```{r}
ADF_KPSS <- matrix(nrow=2,ncol = length(composite_ts))
for (i in 1:length(composite_ts)) {
  temp <- adf.test(diff(ts1[,i],1))
  temp2 <- kpss.test(diff(ts1[,i],1))
  ADF_KPSS[1,i]<- temp$p.value
  ADF_KPSS[2,i]<-temp2$p.value
}
ADF_KPSS

```

Lost the unit root from KPSS, so order of integration is 1

```{r}
VARselect(ts1[,8],lag=20,type="both")
```

AIC says lag level is 3 or 5

let's test 3

```{r}
V.3<-VAR(ts1,p=3,type="both")
serial.test(V.3)
```

and 5

```{r}
V.5<-VAR(ts1,p=5,type="both")
serial.test(V.5)
```

Still serial correlation in the residuals, so let's increase

```{r}
V.8<-VAR(ts1,p=8,type="both")
serial.test(V.8)
```

8 is the best, but still p-value <0.05

```{r}
#Stability analysis
1/roots(V.5)[[1]] # ">1"
1/roots(V.5)[[2]] # ">1"

#Alternative stability analyis
plot(stability(V.5)) ## looks fine
```

Stability is fine at 5


```{r}
GC_results <- granger.test(ts1,5)
GC_results_bool <- GC_results
pvalue=0.01/12
GC_results_bool[,1] <- GC_results_bool[,2] < pvalue

par(mar = c(15, 5, 5, 1), mfrow = c(1, 1), mgp = c(2.5, 1, 0))
barplot(GC_results_bool[,1], las=2,cex.names=0.8)
```

```{r}
varlst <- colnames(composite_ts)
GC_results_Fstat <- matrix(nrow=length(varlst),ncol=length(varlst))

counter=1;
for (i in 1:dim(GC_results)[1]){
	if (!(i%%(length(varlst)-1))){
		constant=(length(varlst)-1)
	} else {
	constant = i%%(length(varlst)-1)}
	if (constant>=counter){
			constant=1+constant
			}
		else{
			constant=0+constant
			}
	
	if (GC_results[i,2]<pvalue){
		GC_results_Fstat[counter,constant] <- GC_results[i,1]
	} 
	 else {
		 GC_results_Fstat[counter,constant] <- NA
	 }
	if (!(i%%(length(varlst)-1))){
		counter <- counter+1
	}
}
GC_results_Fstat[is.na(GC_results_Fstat)] <- 0
rownames(GC_results_Fstat) <- varlst
colnames(GC_results_Fstat) <- varlst
GC_results_Fstat <- round(GC_results_Fstat, digits=2)
library('gplots')

my_palette <- colorRampPalette(c("black", "red", "yellow"))(n = 29)
col_breaks = c(seq(0,1,length=10), # for red
seq(1.1,max(GC_results_Fstat)/2,length=10),  # for yellow
seq(max(GC_results_Fstat)/2+0.01,max(GC_results_Fstat),length=10)) # for green

lmat = rbind(c(0,3),c(2,1),c(0,4))
lwid = c(1.5,4)
lhei = c(1.5,4,1)
heatmap.2(GC_results_Fstat,
  cellnote = GC_results_Fstat,  # same data set for cell labels  
  notecol="black",      # change font color of cell labels to black
  density.info="none",  # turns off density plot inside color legend
  trace="none",         # turns off trace lines inside the heat map
  margins =c(10,10),     # widens margins around plot
  col=my_palette,       # use on color palette defined earlier
  breaks=col_breaks,    # enable color transition at specified limits
  dendrogram="none",     # only draw a row dendrogram
  Colv="NA",
  notecex=2,
          cexRow=2,
          cexCol=2,
		  key.xlab="",
		  lmat=lmat,
		  lwid=lwid,
		  lhei=lhei	 
  )
```

```{r}
library(igraph)
net <- graph.adjacency(t(GC_results_Fstat), mode="directed", weighted=TRUE)
igraph::write.graph(net,'ClusterGraph.xml',format='graphml')
plot(net, edge.label=round(E(net)$weight, 3))

autocurve.edges2 <-function (graph, start = 0.5)
{
    cm <- count.multiple(graph)
    mut <-is.mutual(graph)  #are connections mutual?
    el <- apply(get.edgelist(graph, names = FALSE), 1, paste,
	collapse = ":")
    ord <- order(el)
    res <- numeric(length(ord))
    p <- 1
    while (p <= length(res)) {
        m <- cm[ord[p]]
        mut.obs <-mut[ord[p]] #are the connections mutual for this point?
        idx <- p:(p + m - 1)
        if (m == 1 & mut.obs==FALSE) { #no mutual conn = no curve
            r <- 0
		}
        else {
            r <- seq(-start, start, length = m)
		}
        res[ord[idx]] <- r
        p <- p + m
	}
    res
}

deg <- degree(net, mode="all")
V(net)$size <- deg*1
E(net)$width <- E(net)$weight*0.5
curves <-autocurve.edges2(net)
plot(net, vertex.color="white", edge.label=round(E(net)$weight, 3), edge.curved=curves)
```

